Measurement Bias from Address Aliasing

### 2014-05-29 paper.tex
Fix parentesis error

% See analysis for results showing this does not alias
\begin{figure}
  \begin{lstlisting}[frame=single, xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
#define ALIAS(a, b) \
    (((long)&a) & 0xfff == ((long)&b) & 0xfff)
static int i, j, k;
int main() {
    int g = 0, inc = 1;
    if (ALIAS(inc, i) || ALIAS(g, i))
        return main();
    for (; g < 65536; g++) {
        i += inc;
        j += inc;
        k += inc;
    }
    return 0;
}
  \end{lstlisting}
  \caption{Dynamically detect aliasing case, and avoid by pushing another stack frame.}
  \label{lst:loopfixed}
\end{figure}

>>>>

% See analysis for results showing this does not alias
\begin{figure}
  \begin{lstlisting}[frame=single, xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
#define ALIAS(a, b) \
    ((((long)&a) & 0xfff) == (((long)&b) & 0xfff))
static int i, j, k;
int main() {
    int g = 0, inc = 1;
    if (ALIAS(inc, i) || ALIAS(g, i))
        return main();
    for (; g < 65536; g++) {
        i += inc;
        j += inc;
        k += inc;
    }
    return 0;
}
  \end{lstlisting}
  \caption{Dynamically detect aliasing case, and avoid by pushing another stack frame.}
  \label{lst:loopfixed}
\end{figure}
